Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-11-13 journal/ms.Rmd
minor corrections

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlates between connectivity in the end-state network and AoA is an important blusprint of both EXT and INT. If there is no such correlation, neither growth scenarios can be posited as a learning mechanism.

>>>>

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA is an important blueprint of both EXT and INT. If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.

### 2018-11-13 journal/ms.tex
minor corrections

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also compatible with INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlates between connectivity in the
end-state network and AoA is an important blusprint of both EXT and INT.
If there is no such correlation, neither growth scenarios can be posited
as a learning mechanism.

>>>>

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also compatible with INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlation between connectivity in the
end-state network and AoA is an important blueprint of both EXT and INT.
If there is no such correlation, neither growth scenarios can be posited
as a possible learning mechanism.
